---
title: "ggpval user guide"
author: "Jun Cheng"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ggpval

`ggpval` allow you to generate statistic test and add test p-value to plots automatically. P-valules can be presented as formated p-values or with stars (e.g. *, **). Alternatively one can also annotation groups with text.

## Installation

You can install ggpval from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("s6juncheng/ggpval")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## Example

Simulate data with groups.

```{r, fig.show='hold'}
library(ggpval)
library(data.table)
library(ggplot2)
A <- rnorm(200, 0, 3)
B <- rnorm(200, 2, 4)
G <- rep(c("G1", "G2"), each = 100)
dt <- data.table(A, B, G)
dt <- melt(dt, id.vars = "G")
```


## A trivial boxplot example

Give group pairs you want to compare in `pairs`.

```{r, echo=TRUE, results='asis'}
plt <- ggplot(dt, aes(variable, value)) +
  geom_boxplot() +
  geom_jitter()

add_pval(plt, pairs = list(c(1, 2)))
```

## Boxplot with facets

```{r, echo=TRUE, results='asis'}
plt <- ggplot(dt, aes(variable, value)) +
  geom_boxplot() +
  geom_jitter() +
  facet_wrap(~G)
add_pval(plt, pairs = list(c(1, 2)))
```
